Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-12 paper/aldebaran.tex
specify both parallax and angular diameter explicitly

\section{Aldebaran}
Aldebaran is a red giant star with spectral type K5, one of the nearest such stars at a distance of only $19.96 \pm 0.38$~pc \citep{hipparcos}. Its position near the Ecliptic permits the determination of its angular diameter by lunar occultations and by interferometry \citep[$20.58 \pm 0.03$ mas;][]{richichi2005,1979ApJ...228L.111B,brown1979,panek1980}. These tight constraints are valuable in breaking degeneracies in stellar modelling and make this an ideal star for asteroseismic characterization (Appendix~/ref{sec:mod}).

@@

The final constraint available for Aldebaran is the angular diameter of the star, measured by long baseline interferometry, combined with the parallax to produce a physical radius constraint of $R_{\textrm{int}}=44.2\pm0.9\textrm{R}_{\odot}$ \citep{richichi2005}.

>>>>

\section{Aldebaran}
Aldebaran is a red giant star with spectral type K5, one of the nearest such stars at a distance of only $19.96 \pm 0.38$~pc as determined by \hipparcos \citep{hipparcos}. Its position near the Ecliptic permits the determination of its angular diameter by lunar occultations and by interferometry \citep[$20.58 \pm 0.03$ mas;][]{richichi2005,1979ApJ...228L.111B,brown1979,panek1980}. These tight constraints are valuable in breaking degeneracies in stellar modelling and make this an ideal star for asteroseismic characterization (Appendix~/ref{sec:mod}).

@@

The final constraint available for Aldebaran is the angular diameter of the star as measured by long baseline interferometry and lunar occultations \citep[$20.58 \pm 0.03$ mas;][]{richichi2005,1979ApJ...228L.111B,brown1979,panek1980}, combined with the \hipparcos parallax of $19.96 \pm 0.38$~pc to produce a physical radius constraint of $R_{\textrm{int}}=44.2\pm0.9\textrm{R}_{\odot}$.
